---
title: "Forecasting Pix Across Brazil: Global Models and Coherent Geographic Reconciliation"
author:
  - name: "Author name"
    affiliation: "Affiliation"
format:
  pdf:
    number-sections: true
    keep-tex: true
    include-in-header: preamble.tex
execute:
  echo: false
  warning: false
  cache: false
---

```{r}
#| label: setup
#| include: false
include_tex <- function(path) {
  if (!file.exists(path)) {
    safe_path <- gsub("_", "\\\\_", path, fixed = TRUE)
    return(knitr::asis_output(paste0(
      "\\begin{quote}\\textit{Output not generated yet: ",
      safe_path,
      ".}\\end{quote}"
    )))
  }
  knitr::asis_output(paste(readLines(path, warn = FALSE), collapse = "\n"))
}

include_figure <- function(path) {
  if (!file.exists(path)) {
    safe_path <- gsub("_", "\\\\_", path, fixed = TRUE)
    return(knitr::asis_output(paste0(
      "\\begin{quote}\\textit{Figure not generated yet: ",
      safe_path,
      ".}\\end{quote}"
    )))
  }
  knitr::include_graphics(path)
}

prefer_national <- function(national_path, pilot_path) {
  if (file.exists(national_path)) national_path else pilot_path
}
```

## Abstract

<!-- Write last. Report the problem, data, rolling-origin design, main quantitative result, and contribution in 180–220 words. -->

## Introduction

<!-- Motivate municipal Pix forecasting; define the gap; state the research question and four contributions. -->

## Related Work

### Pix and instant payments as digital infrastructure

### Global forecasting of many related time series

### Hierarchical forecast reconciliation

### Structural breaks and forecast reliability

## Data and Forecasting Problem

### Official data sources

```{r}
#| label: tbl-data-coverage
#| results: asis
include_tex("output/tables/table_data_coverage.tex")
```

### Target definition

The primary target is the monthly number of outgoing Pix transactions:

$$
y_{i,t} = QT\_PagadorPF_{i,t} + QT\_PagadorPJ_{i,t}.
$$

### Stable geographic hierarchy

### Forecasting task

```{r}
#| label: fig-pix-national
#| fig-cap: "Evolution of outgoing Pix transactions in Brazil."
include_figure("output/figures/figure_pix_evolution_national.pdf")
```

```{r}
#| label: fig-pix-regions
#| fig-cap: "Evolution of outgoing Pix transactions across macroregions."
include_figure("output/figures/figure_pix_evolution_regions.pdf")
```

## Methods

### Local statistical baselines

### Global forecasting models

```{r}
#| label: tbl-global-model-parameters
#| results: asis
include_tex(prefer_national(
  "output/tables/table_global_model_parameters_national.tex",
  "output/tables/table_global_model_parameters_pilot_alagoas_roraima.tex"
))
```

### Forecast reconciliation

### Structural-break diagnostics

```{r}
#| label: fig-structural-breaks
#| fig-cap: "Structural-break diagnostics for national Pix activity."
include_figure("output/figures/figure_structural_breaks.pdf")
```

## Experimental Design

```{r}
#| label: tbl-experimental-design
#| results: asis
include_tex("output/tables/quadro_experimental_design.tex")
```

### Rolling-origin validation

### Accuracy metrics

### Statistical comparison and ablations

## Forecasting Results

### Overall model comparison

```{r}
#| label: tbl-municipal-accuracy
#| results: asis
include_tex("output/tables/table_forecast_accuracy_municipal.tex")
```

```{r}
#| label: fig-accuracy-horizon
#| fig-cap: "Municipality-level forecast accuracy by model and horizon."
include_figure("output/figures/figure_accuracy_by_horizon.pdf")
```

### Value of global learning

```{r}
#| label: tbl-relative-gain
#| results: asis
include_tex("output/tables/table_relative_gain.tex")
```

```{r}
#| label: fig-relative-gain
#| fig-cap: "Forecast gains relative to the seasonal-naive benchmark."
include_figure("output/figures/figure_relative_gain.pdf")
```

### Value and computational cost of reconciliation

```{r}
#| label: tbl-hierarchy-accuracy
#| results: asis
include_tex("output/tables/table_forecast_accuracy_hierarchy.tex")
```

```{r}
#| label: tbl-newey-west
#| results: asis
include_tex("output/tables/table_newey_west_comparison.tex")
```

```{r}
#| label: tbl-runtime
#| results: asis
include_tex("output/tables/table_runtime.tex")
```

### Robustness checks

```{r}
#| label: tbl-scaled-metric-coverage
#| results: asis
include_tex("output/tables/table_scaled_metric_coverage.tex")
```

```{r}
#| label: tbl-negative-predictions
#| results: asis
include_tex("output/tables/table_negative_predictions.tex")
```

```{r}
#| label: fig-error-distribution
#| fig-cap: "Distribution of scaled absolute forecast errors."
include_figure("output/figures/figure_error_distribution.pdf")
```

## Geographic Regimes and Forecast Reliability

```{r}
#| label: fig-forecast-gain-map
#| fig-cap: "Spatial distribution of XGBoost forecast gains relative to the seasonal-naive benchmark at horizon one."
include_figure(prefer_national(
  "output/figures/figure_forecast_gain_map_national_h1.pdf",
  "output/figures/figure_forecast_gain_map_pilot_alagoas_roraima_h1.pdf"
))
```

```{r}
#| label: tbl-forecast-reliability
#| results: asis
include_tex(prefer_national(
  "output/tables/table_forecast_reliability_national.tex",
  "output/tables/table_forecast_reliability_pilot_alagoas_roraima.tex"
))
```

```{r}
#| label: tbl-xgboost-shap
#| results: asis
include_tex(prefer_national(
  "output/tables/table_xgboost_shap_national.tex",
  "output/tables/table_xgboost_shap_pilot_alagoas_roraima.tex"
))
```

```{r}
#| label: fig-xgboost-shap
#| fig-cap: "Mean absolute TreeSHAP contributions for the global XGBoost model estimated in R."
include_figure(prefer_national(
  "output/figures/figure_xgboost_shap_national.pdf",
  "output/figures/figure_xgboost_shap_pilot_alagoas_roraima.pdf"
))
```

## Discussion and Limitations

## Conclusion

## Data and Code Availability

<!-- Insert the archived code release, extraction vintage, and official-source links at submission. -->
